%%%% kr-instructions.tex -- version 1.3 (11-Jan-2021)

% \typeout{KR2024 Instructions for Authors}

% These are the instructions for authors for KR-24.

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in

\usepackage{kr}

% Use the postscript times font!
\usepackage{times}

\usepackage{settings}
\input{macros}

\urlstyle{same}

% the following package is optional:
%\usepackage{latexsym}

% See https://www.overleaf.com/learn/latex/theorems_and_proofs
% for a nice explanation of how to define new theorems, but keep
% in mind that the amsthm package is already included in this
% template and that you must *not* alter the styling.
% \newtheorem{example}{Example}
% \newtheorem{theorem}{Theorem}

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission.

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.
%PDF Info Is REQUIRED.
\pdfinfo{
/TemplateVersion (KR.2022.0, KR.2023.0, KR.2024.0)
}



\title{How Lucky Are You to Know Your Way?\par A Probabilistic Approach to Knowing How Logics}

% Single author syntax
\iffalse % (remove the multiple-author syntax below and \iffalse ... \fi here)
\author{%
    Author name
    \affiliations
    Affiliation
    \emails
    email@example.com    % email
}
\fi
% Multiple author syntax
\author{%
Valentin Cassano$^{1,3}$\and
Pablo F. Castro$^{1,3}$\and
Pedro R. D'Argenio$^{2,3}$\and
Raul Fervari$^{2,3}$ \\
\affiliations
$^1$Universidad Nacional de R\'io Cuarto, Argentina\\
$^2$Universidad Nacional de C\'ordoba, Argentina\\
$^3$Consejo Nacional de Investigaciones Cient\'ificas y T\'ecnicas (CONICET), Argentina\\
\emails
\{valentin, pcastro\}@dc.exa.unrc.edu.ar,
\{pedro.dargenio, rfervari\}@unc.edu.ar
}

\begin{document}

\maketitle
\pedro{- puse subtitulo para considerar\\- cambi\'e el orden de las filiaciones}

\begin{abstract}
  In this paper we introduce a probabilistic version of knowing-how modal logics.  More precisely,  our logics extend extant approaches to model the ability of an agent to achieve a given goal with a certain probability.  On the semantics side,  we enrich the models of the logic with probability distributions over the agent's actions.  We investigate different variants of this formalism.  First,  we consider a probabilistic version of the linear plan-based logic of knowing how, and discuss its properties. Then, we consider indistinguishably classes,  and obtain two logics,  one that has `non-adaptative' plans, and another  with `adaptative' plans. For these logics we investigate the computational complexity of their model-checking problem, obtaining uncedidability results for the first and the second logic, while for the last one the problem is decidable in polynomial time.  We implemented a prototype tool of the model-checking algorithm for the decidable case which we used to analyse some case studies.
\end{abstract}

\input{introduction}
\input{preliminaries}
\input{kh-linearplans}
\input{kh-probabilistic}
\input{final}

\section*{Acknowledgments}

This work was supported by Agencia I$+$D$+$i grants PICT 2022-09-00580
({\scriptsize CoSMoSS}) and 
2021-00400,
%
the EU H2020 research and innovation programme
under the Marie Sk{\l}odowska-Curie grant agreements 101008233
({\scriptsize MISSION}),
%
the IRP SINFIN, 
%
and SeCyT-UNC grants 33620230100384CB ({\scriptsize MECANO}) and 33620230100178CB.
%
\textcolor{red}{completar}



\bigpedro{copiar todas las bibtex entry de dblp (incluyendo DOI) salvo las que no est\'en ah\'i :-)}




%% The file kr.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{kr}
\bibliography{references}


\appendix

\input{appendix}


\end{document}

